
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Saeid Haghighipour} 
  & Email : haghighi.pour.sa@gmail.com\\
  & Mobile : +98-990-866-2022
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Sharif University of Technology}{Tehran, Iran}
      {Master of Science in Electrical and Electronics}{Sep. 2020 -- Aug. 2023}
    \resumeSubheading
      {University of Tehran}{Tehran, Iran}
      {Bachelor of Engineering in Electrical and Electronics}{Sep. 2016 -- Aug. 2020}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Advanced Electronics Group}{Tehran, Iran}
      {Embedded Linux Engineer}{Mar 2023 - Present}
      
    \resumeSubheading
      {Amin Nano Systems}{Tehran, Iran}
      {Embedded Software Engineer}{Mar 2021 - Feb 2023}

    \resumeSubheading
      {Samaneh Payesh Ghodrat}{Tehran, Iran}
      {Electronics Technician}{Mar 2018 - Jan 2020}

    \resumeSubheading
      {University of Tehran}{Tehran, Iran}
      {Embedded Systems Course Teaching Assistant}{Sep 2017 - Oct 2017}
      
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Smart Lighting System}
      {An intelligent system based on NRF technology and cloud platforms.}
    \resumeSubItem{TPMS Software and Hardware Design}
      {Temperature and Pressure Monitoring System for car tires. }
    \resumeSubItem{Smart Gas Meter}
      {Designed and implemented for National Iranian Gas Company.}
    \resumeSubItem{Asset Tracking System}
      {A system based on LoRa technology aimed at optimizing power consumption.}
    \resumeSubItem{Remote Drone}
      {Design a low latency Drone communication system so that pilot can control it over Internet.}
    \resumeSubItem{Smart Home Gateway}
      {A Zigbee based gateway with voice assistant capability for Smart home.}
    \resumeSubItem{LoRa Solution}
      {Design and implement software of a LoRa network from end device to LoRa Network Server(LNS).}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{\textbf{Languages}{: Python, C, C++, Embedded C, Assembly, Cuda}}
    \item{\textbf{Embedded Systems}{: ST, TI, ESPressif and Microchip single core and dual core MCUs progrmmaing, Bare Metal programming, Single Board Computers, FreeRTOS}}
    \item{\textbf{General Linux}{: GNU toolchain, Firewalls(iptables, ufw), Kernel and Driver development, Networking, Bash scripting, Buildroot, LFS}}
    \item{\textbf{Tools and Technologies}{: Keil, CodeVision, MATLAB and Simulink, Altium Designer, Proteus, Git, MQTT, LoRa, FPGA development, GPU and Parallel processing}}
    
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}